Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-14 chi2013-webbox.tex
abstract short

For the B conditions we prepared, for each dataset condition in each task, a spreadsheet listing key statistics for each of the relevant candidates (e.g., universities or restaurants) assembled from each of a pre-selected set of 6 popular data sources (university and restaurant guides), and collated them into Excel spreadsheets.

>>>>

For the B conditions, we prepared a spreadsheet listing key statistics for each of the relevant candidates (e.g., universities or restaurants) using data from of a pre-selected set of 6 popular data sources (university and restaurant guides), and collated them into Excel spreadsheets.
